An Image-based method for phase estimation, gating and temporal super-resolution of \\cardiac ultrasound

### 2017-02-21 paper155.tex
Added tables into latex file

	A representative single-cycle video of the subject's heart-beat can now be reconstructed by sampling the manifold $M(\phi)$ at any desired resolution from the range $[0, 1)$ of the cardiac phase. Note that this approach will facilitate temporal super-resolution only if the set of images observed in each distinct period of the given image sequence differ in cardiac phase by some non-zero amount. Also, the amount of temporal super-resolution possible will depend both on the number of cycles captured and the amount by which one can expect the corresponding images to be perturbed in phase across cycles. 
%\vspace{-0.5cm}
\section{Results}
\label{sec:results}
%
%
\begin{IonFigT}
\centering
%
\includegraphics[width=5.0in]{figures/decoded/2015-07-27-10-36-06_2015-07-15-16-56-16_1.raw.bmode/phaseordered.png}
\ionbox{5.0in}\\
%
\caption{Visualization of m-mode frames ordered by estimated cardiac phase}
\label{fig:phase_ordering}
\end{IonFigT}
%
%
%\vspace{-0.5cm}
\section{Discussion and future work}
\label{sec:discussion}
%

>>>>

	A representative single-cycle video of the subject's heart-beat can now be reconstructed by sampling the manifold $M(\phi)$ at any desired resolution from the range $[0, 1)$ of the cardiac phase. Note that this approach will facilitate temporal super-resolution only if the set of images observed in each distinct period of the given image sequence differ in cardiac phase by some non-zero amount. Also, the amount of temporal super-resolution possible will depend both on the number of cycles captured and the amount by which one can expect the corresponding images to be perturbed in phase across cycles. 
%\vspace{-0.5cm}
\section{Results}
\label{sec:results}
%
\begin{table}[h]
\centering
\begin{tabular}{|c|c|c|c|}
\hline
VID & $R^2$ & Mean $\pm$ Std & Median $\pm$ IQR \\ \hline
1 & 0.9995 & 1.55 $\pm$ 0.89 & 1.00 $\pm$ 1.00 \\ \hline
2 & 0.9995 & 1.36 $\pm$ 1.15 & 1.00 $\pm$ 2.00 \\ \hline
3 & 0.9996 & 1.45 $\pm$ 0.89 & 2.00 $\pm$ 1.00 \\ \hline
4 & 0.9998 & 0.73 $\pm$ 0.62 & 1.00 $\pm$ 1.00 \\ \hline
5 & 0.9990 & 2.09 $\pm$ 1.78 & 1.00 $\pm$ 2.00 \\ \hline
6 & 0.9992 & 1.40 $\pm$ 1.74 & 1.00 $\pm$ 0.75 \\ \hline
\end{tabular}
\caption{My caption}
\label{my-label}
\end{table}
%
\begin{table}[h]
\centering
\begin{tabular}{|c|c|c|}
\hline
\begin{tabular}[c]{@{}c@{}}\\ VID \end{tabular} & \begin{tabular}[c]{@{}c@{}}LOOCV (50) NCORR\\ Mean $\pm$ Std\end{tabular} & \begin{tabular}[c]{@{}c@{}}QRS Peak Frame NCORR\\ Mean $\pm$ Std\end{tabular} \\ \hline
1 & 0.8562 $\pm$ 0.0366 & 0.7981 $\pm$ 0.0532 \\ \hline
2 & 0.8558 $\pm$ 0.0525 & 0.7877 $\pm$ 0.0503 \\ \hline
3 & 0.8592 $\pm$ 0.0348 & 0.7849 $\pm$ 0.0457 \\ \hline
4 & 0.8713 $\pm$ 0.0348 & 0.8395 $\pm$ 0.0486 \\ \hline
5 & 0.8655 $\pm$ 0.0312 & 0.8196 $\pm$ 0.0476 \\ \hline
6 & 0.8736 $\pm$ 0.0278 & 0.8270 $\pm$ 0.0778 \\ \hline
\end{tabular}
\caption{My caption}
\label{my-label}
\end{table}
%
\begin{IonFigT}
\centering
%
\includegraphics[width=5.0in]{figures/decoded/2015-07-27-10-36-06_2015-07-15-16-56-16_1.raw.bmode/phaseordered.png}
\ionbox{5.0in}\\
%
\caption{Visualization of m-mode frames ordered by estimated cardiac phase}
\label{fig:phase_ordering}
\end{IonFigT}
%
%
%\vspace{-0.5cm}
\section{Discussion and future work}
\label{sec:discussion}
%
